PROTEST

### 2019-12-05 article/main.tex
labels and rdg --> Rdg

    \begin{equation}\label{si}
      si_i \sim \Gamma(\alpha, \frac{\alpha}{\widehat{si_i}})
    \end{equation}

@@

  \begin{multline}\label{gfir-spruce}
    \widehat{P_{Gfir,i}} = logit(a + b_1 alti_i + b_2 slope_i + b_3 rum_i + b_4 pH_i + b_5 expoNS_i + b_6 expoEW_i + \\ b_7 dg_i + b_8 g_i + b_9 greco_i + b_{10} hyrdo_i + b_{11} carbo_i)
  \end{multline}

  \begin{equation}\label{}
    P_{Gfir,i} \sim \mathcal{B}e (\widehat{P_{Gfir,i}}\phi, (1-\widehat{P_{Gfir,i}})\phi)
  \end{equation}

@@

  \begin{multline}\label{gfir-spruce}
    \widehat{R_{Dg, i}} = a + b_1 alti_i + b_2 slope_i + b_3 rum_i + b_4 pH_i + b_5 expoNS_i + b_6 expoEW_i + \\ b_7 dg_i + b_8 g_i + b_9 greco_i + b_{10} hyrdo_i + b_{11} carbo_i
  \end{multline}

  \begin{equation}\label{si}
    R_{Dg, i} \sim \Gamma(\alpha, \frac{\alpha}{\widehat{R_{Dg, i}}})
  \end{equation}

@@

\begin{equation}\label{three}\tag{c}
  \bullet \frac{Dg_i}{Dg_j} = r_{Dg}
\end{equation}

\noindent where $r_{Dg}$ is calculated by adding to the models predictions (models described at eqn \ref{DgModel}) a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals (see the \textit{Species quadratic diameter} section).

@@

\noindent Using equation \ref{three}, $Dg_i^2 / Dg_j^2$ can be replaced by $r_{Dg}^2$:

\begin{equation*}\label{}
  Dg_t^2(G_i + r_{Dg}^2G_j^2)= Dg_i^2(G_i + G_j)
\end{equation*}

@@

\begin{equation*}\label{}
  Dg_i = Dg_t\sqrt{\frac{G_i + r_{Dg}^2G_j}{G_i + G_j}}
\end{equation*}

>>>>

    \begin{equation}\label{siGamma}
      si_i \sim \Gamma(\alpha, \frac{\alpha}{\widehat{si_i}})
    \end{equation}

@@

  \begin{multline}\label{g}
    \widehat{P_{Gfir,i}} = logit(a + b_1 alti_i + b_2 slope_i + b_3 rum_i + b_4 pH_i + b_5 expoNS_i + b_6 expoEW_i + \\ b_7 dg_i + b_8 g_i + b_9 greco_i + b_{10} hyrdo_i + b_{11} carbo_i)
  \end{multline}

  \begin{equation}\label{gBeta}
    P_{Gfir,i} \sim \mathcal{B}e (\widehat{P_{Gfir,i}}\phi, (1-\widehat{P_{Gfir,i}})\phi)
  \end{equation}

@@

  \begin{multline}\label{DgModel}
    \widehat{R_{Dg, i}} = a + b_1 alti_i + b_2 slope_i + b_3 rum_i + b_4 pH_i + b_5 expoNS_i + b_6 expoEW_i + \\ b_7 dg_i + b_8 g_i + b_9 greco_i + b_{10} hyrdo_i + b_{11} carbo_i
  \end{multline}

  \begin{equation}\label{DgGamma}
    R_{Dg, i} \sim \Gamma(\alpha, \frac{\alpha}{\widehat{R_{Dg, i}}})
  \end{equation}

@@

\begin{equation}\label{three}\tag{c}
  \bullet \frac{Dg_i}{Dg_j} = R_{Dg}
\end{equation}

\noindent where $R_{Dg}$ is obtained by drawing a random number from the Gamma distribution $\Gamma(\alpha, \frac{\alpha}{\widehat{R_{Dg, p}}})$ (see the \textit{Species quadratic diameter} section).

@@

\noindent Using equation \ref{three}, $Dg_i^2 / Dg_j^2$ can be replaced by $R_{Dg}^2$:

\begin{equation*}\label{}
  Dg_t^2(G_i + R_{Dg}^2G_j^2)= Dg_i^2(G_i + G_j)
\end{equation*}

@@

\begin{equation*}\label{}
  Dg_i = Dg_t\sqrt{\frac{G_i + R_{Dg}^2G_j}{G_i + G_j}}
\end{equation*}
